---
title: 'Statistical Inference Course Project: Part 2'
author: "Dongying"
date: "8/20/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Basic Inferential Data Analysis Instructions
Now in the second portion of the project, I'm going to analyze the ToothGrowth data in the R datasets package.  

First, let's load the ToothGrowth data and perform some basic exploratory data analyses
Provide a basic summary of the data.
```{r, loadData, cache=TRUE}
library(datasets)
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
summary(ToothGrowth)
```
We can also make a box plot to see how the tooth growth length is related to supp and dose:
```{r, fig2, fig.height=3, fig.width=5}
library(ggplot2)
ggplot(data = ToothGrowth, aes(x = as.factor(dose), y = len, fill = supp)) +
    geom_boxplot() +
    xlab("Dose(mg)") +
    ylab("Tooth growth length")
```

Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose.
### Hypothesis 1:
Two supplies have the same influence to the tooth growth over the whole dose range.
```{r}
test_supp1 <- t.test(len ~ supp, data = ToothGrowth)
test_supp1$conf.int
test_supp1$p.value
```
The confidence interval includes 0 and p value is greater than 0.05. Fail to reject hypo 1. Can't tell the difference.

### Hypothesis 2:
Two supplies have the same influence to the tooth growth with 0.5 mg dosage.
```{r}
test_supp2 <- t.test(len ~ supp, data = subset(ToothGrowth, dose == 0.5))
test_supp2$conf.int
test_supp2$p.value
```
The confidence interval is greater than 0 and p value is smaller than 0.05. Reject hypo 2. OJ performs better than VC with 0.5 mg dosage.

### Hypothesis 3:
Two supplies have the same influence to the tooth growth with 1.0 mg dosage.
```{r}
test_supp3 <- t.test(len ~ supp, data = subset(ToothGrowth, dose == 1.0))
test_supp3$conf.int
test_supp3$p.value
```
The confidence interval is greater than 0 and p value is smaller than 0.05. Reject hypo 3. OJ performs better than VC with 1.0 mg dosage.

### Hypothesis 4:
Two supplies have the same influence to the tooth growth with 2.0 mg dosage.
```{r}
test_supp4 <- t.test(len ~ supp, data = subset(ToothGrowth, dose == 2.0))
test_supp4$conf.int
test_supp4$p.value
```
The confidence interval includes 0 and p value is greater than 0.05. Fail to reject hypo 4. Can't tell the difference.

## Conculsion
OJ performs better than VC for dosages 0.5 & 1.0 mg. OJ and VC gives the same amount of tooth growth for dose amount 2.0 mg. 



